### 2020-03-28 probabilisticProgrammingMartingales.tex
Fix F(M -> N) conversion formula

\subsection{Alternative Semantics}
\akr{This version of the semantics is much more convenient for allowing multiple different reduction orders. I don't currently have a proof of the equivalence of this with the more usual semantics. I expect that that would be somewhat complicated, but not terribly difficult. I don't know whether a semantics like this has already been defined elsewhere. I just thought I'd write it out so you can see it and in case I use it later. If I do end up actually using it I'll write it up nicer, but hopefully this is at least enough for you to understand what I mean.}

@@

For any reduction \akr{including reductions not included in the definition above, i.e.~out of order reductions} $M \to N$, define a corresponding map $F(M \to N) : F(N) \to F(M)$ induced (as a magma morphism) by the obvious injection along with the replacements
\begin{align*}
F(E[(\lambda x. F[x_i])G[y]] \to E[F(G[y]/x)[G[y_i]]]) (x_i \cdot y) & = y_i\\
F(E[\tY_i F[y]] \to E[F[y_0] (\tY F[y])]) (y_0) & = \tY_i \cdot y
\end{align*}
where $y$ can be any of the things in $L(N)$.

>>>>

\subsection{Alternative Semantics}
\akr{This version of the semantics is much more convenient for allowing multiple different reduction orders. I don't currently have a proof of the equivalence of this with the more usual semantics. I expect that that would be somewhat complicated, but not terribly difficult. I don't know whether a semantics like this has already been defined elsewhere. I just thought I'd write it out so you can see it and in case I use it later. If I do end up actually using it I'll write it up nicer, but hopefully this is at least enough for you to understand what I mean.

Having thought a bit more about this, I realise it may not be quite right. I'll see if I can fix it later.}

@@

For any reduction \akr{including reductions not included in the definition above, i.e.~out of order reductions} $M \to N$, define a corresponding map $F(M \to N) : F(N) \to F(M)$ induced (as a magma morphism) by the obvious injection along with the replacements
\begin{align*}
F(E[(\lambda x. F[x_i])G[y]] \to E[F(G[y]/x)[G[y_i]]]) y_i & = (x_i \cdot y)\\
F(E[\tY_i F[y]] \to E[F[y] (\tY F[y_0])]) (y_0) & = \tY_i \cdot y
\end{align*}
where $y$ can be any of the things in $L(N)$.
